### 2019-06-25 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits_appendix.tex
Typo
Update and fix typos

% \paragraph{Number of switches.}\label{app:5:NumberSwitches}
% %
% Note that we controlled the total number of transitions $(2)$, $(3)$ and $(5)$,
% which are the only transitions when a player can switch from arm $k$ to arm $k'\neq k$.
% Thus, the total number of arm switches is also proved to be logarithmic, if all players uses
% the \MCTopM-\klUCB{} algorithm.

% \paragraph{Strong uniform efficiency.}\label{app:5:JustifyingDefinition5}
% %
% As soon as $R_T = \bigO{\log T}$ for all problem, \MCTopM{} is clearly proved
% to be uniformly efficient, as $\log T$ is $\smallO{T^{\alpha}}$ for any $\alpha\in(0,1)$.
% %
% And as justified after Definition~\ref{def:5:DecentralizedUniformEfficiency} (page~\pageref{def:5:DecentralizedUniformEfficiency}), uniform efficiency and invariance under permutations of the users implies strong uniform efficiency, and so \MCTopM{} satisfies Definition~\ref{def:5:DecentralizedUniformEfficiency}.
% %
% This is a sanity check: the lower-bound of
% Theorem~\ref{thm:5:BetterLowerBound} indeed applies to our algorithm \MCTopM,
% and finally this highlights that it is order-optimal for the regret, in the sense that it matches the lower-bound up-to a multiplicative constant,
% and optimal for the term \ref{eq:5:term1}.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.95\textwidth]{Comparison_of_our_lowerbound_and_Anandkumar_2010__9_arms.pdf}
  \caption[Comparison of our lower bound against the one from \cite{Zhao10}]{Comparison of our lower bound against the one from \cite{Zhao10}, on a simple problem with $9$ Bernoulli arms, of means $\boldsymbol{\mu} = [0.1, 0.2, \dots, 0.9]$, as a function of the number of players $M$.}
  \label{fig:5:CompLowerBounds}
\end{figure}

@@

%
% System regret and three terms
%
\begin{figure}[!h]
    \centering
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_2092905764868974160.pdf}
    % \end{subfigure}
    % ~
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_1699475021767911583.pdf}
    % \end{subfigure}
    \caption[Illustrating the decomposition of the multi-players regret with its three terms]{The three terms \ref{eq:5:term1}, \ref{eq:5:term2}, \ref{eq:5:term3} of the multi-players regret, and lower bounds \eqref{eq:5:ourLowerBound} and \eqref{eq:5:Zhao10LowerBound} in \textbf{black}, for \Selfish-\klUCB: $M=6$ and $M=9$ players, $K=9$ arms, horizon $T=10000$ (for $1000$ runs).}
    \label{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6}
    % \vspace*{-15pt}  % XXX remove if problem
\end{figure}

>>>>

% \paragraph{Number of switches.}\label{app:5:NumberSwitches}
% %
% Note that we controlled the total number of transitions $(2)$, $(3)$ and $(5)$,
% which are the only transitions when a player can switch from arm $k$ to arm $k'\neq k$.
% Thus, the total number of arm switches is also proven to be logarithmic, if all players uses
% the \MCTopM-\klUCB{} algorithm.

% \paragraph{Strong uniform efficiency.}\label{app:5:JustifyingDefinition5}
% %
% As soon as $R_T = \bigO{\log T}$ for all problem, \MCTopM{} is clearly proven
% to be uniformly efficient, as $\log T$ is $\smallO{T^{\alpha}}$ for any $\alpha\in(0,1)$.
% %
% And as justified after Definition~\ref{def:5:DecentralizedUniformEfficiency} (page~\pageref{def:5:DecentralizedUniformEfficiency}), uniform efficiency and invariance under permutations of the users implies strong uniform efficiency, and so \MCTopM{} satisfies Definition~\ref{def:5:DecentralizedUniformEfficiency}.
% %
% This is a sanity check: the lower-bound of
% Theorem~\ref{thm:5:BetterLowerBound} indeed applies to our algorithm \MCTopM,
% and finally this highlights that it is order-optimal for the regret, in the sense that it matches the lower-bound up-to a multiplicative constant,
% and optimal for the term \ref{eq:5:term1}.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.95\textwidth]{Comparison_of_our_lowerbound_and_Anandkumar_2010__9_arms.pdf}
  \caption[Comparison of our lower bound against the one from \cite{Zhao10}.]{Comparison of our lower bound against the one from \cite{Zhao10}, on a simple problem with $9$ Bernoulli arms, of means $\boldsymbol{\mu} = [0.1, 0.2, \dots, 0.9]$, as a function of the number of players $M$.}
  \label{fig:5:CompLowerBounds}
\end{figure}

@@

%
% System regret and three terms
%
\begin{figure}[!h]
    \centering
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_2092905764868974160.pdf}
    % \end{subfigure}
    % ~
    % \begin{subfigure}[!h]{1.00\textwidth}
        \includegraphics[width=1.00\textwidth]{main_RegretCentralized____env4-4_1699475021767911583.pdf}
    % \end{subfigure}
    \caption[Illustrating the decomposition of the multi-players regret with its three terms.]{The three terms \ref{eq:5:term1}, \ref{eq:5:term2}, \ref{eq:5:term3} of the multi-players regret, and lower bounds \eqref{eq:5:ourLowerBound} and \eqref{eq:5:Zhao10LowerBound} in \textbf{black}, for \Selfish-\klUCB: $M=6$ and $M=9$ players, $K=9$ arms, horizon $T=10000$ (for $1000$ runs).}
    \label{fig:5:MP__M9_K9_T10000_N1000__9_algos__main_RegretCentralized____env6}
    % \vspace*{-15pt}  % XXX remove if problem
\end{figure}
